### 2022-06-18 Submission/STS/Research_Notebook.tex
entries up to 6/17/2022

\begin{figure}[ht!]
\centering
\includegraphics[width=10cm]{auc_trial.png}
\caption{AUC per Trial}
\end{figure}

@@

>>>>

\begin{figure}[ht!]
\label{auc_trial_20}
\centering
\includegraphics[width=10cm]{auc_trial.png}
\caption{AUC per Trial}
\end{figure}

@@

\section{June 13, 2022}

Code Locations: \texttt{APOE-V2/ClinicalBERT/Analysis/ClinicalBERT\_Trial\_Analysis.py} \\ and \texttt{APOE-V2/ClinicalBERT/Models/ClinicalBERT\_Sequence\_Model.py}

First, I created a general \texttt{Trial Analysis} class that I could use for gathering all the needed data from my Optuna studies and applied it to my 50 trial study.

\begin{figure}[h!]
\centering
\includegraphics[width=12cm]{50_trial.png}
\caption{AUC per trial for 50 trial study}
\end{figure}

This graph is similar to the previous graph, as there is no clear trend. Upon looking at the learning rates chosen by Optuna and their corresponding AUCs, all learning rates of form \texttt{x} $\cdot 10^{-5}$ yield the highest AUCs. After trials with this learning rates, the sampler would mysteriously recommend a learning rate much smaller, which resulted in poor performance. The trial analysis spreadsheet is full of such trends, and yet the sampler is unable to pick up on the pattern.

On a separate note, I created a class for the \texttt{ClinicalBERT Sequence Model} for further hyperparameter tuning trials. I am running into a database error which I will address tomorrow.

\section{June 14, 2022}

Code Locations: \texttt{APOE-V2/ClinicalBERT/Models/ClinicalBERT\_Sequence\_Model.py} \\ and \texttt{APOE-V2/ClinicalBERT/Models/ClinicalBERT\_Training\_0616.ipynb}

I fixed the errors with the \texttt{ClinicalBERT Sequence Model} class. The gold standard dataset consists of $\approx$ 6500 annotated sequences with keywords and 500 sequences that contain no keywords. I started training the model with one edit: changing the range of the learning from 1E-6 to 1E-4 as learning rates under 1E-6 inhibited the model's learning.

\section{June 15, 2022}

Code Location: \texttt{APOE-V2/ClinicalBERT/Models/ClinicalBERT\_Training\_0616.ipynb}

I realized that there was an error in the generation of the sequences that did not have a keyword match and had to stop training. The performance was quite similar to the previous study, but I believe there is potential for higher performance with correctly chosen sequences with no keywords.

\section{June 16, 2022}

Code Location: \texttt{APOE-V2/ClinicalBERT/Models/ClinicalBERT\_Training\_0616.ipynb}

I trained on solely the 6500 sequences with a possible range of learning rates from 1E-6 to 1E-3 to further explore the learning rate space. I found the performance was extremely poor (0.5 AUC), as the model was learning too fast and forgetting past knowledge and patterns.

\section{June 17, 2022}

Code Location: \texttt{APOE-V2/ClinicalBERT/Models/ClinicalBERT\_Training\_0616.ipynb} \\ and \texttt{APOE-V2/ClinicalBERT/Preprocessing/Generating\_No\_Keyword\_Sequences.ipynb}

I created the new set of 500 sequences by sampling random 800 character portions from notes and started running a 50 study Optuna trial. The training will finish over the weekend, after which I will conduct a thorough analysis of the loss curves and parameter configurations.
